\begin{cnabstract}
互联网不断发展，其中的信息也随着时间日渐增多，传统的返回检索方式开始无法满足获取所需信息和知识资源的全面性和效率。开放式关系抽取（Open Relation Extraction，ORE）则克服了传统信息获取技术的缺陷，传统的信息获取技术对每种关系模式各自训练了他们的提取器。有很多系统流行于英文的 ORE，例如 OLLIE，ReVerb 和 Exemplar 等。然而，对于其他语言的 ORE 则基本没有相关研究的报告。本毕业设计采用了基于语法分析的系统 ZORE（Zh ORE）来对简体中文文本进行关系和语义模式的抽取。ZORE 从自动解析的依赖树里定义了候选的关系，然后将实体的关系和语义模式不断地通过一种新的双重传播算法。

本文内容包括了

\keywords{开放式关系抽取\enskip ZORE\enskip 双重传播算法}
\end{cnabstract}

\begin{enabstract}
The continuous development of the Internet, where the information is also increasing with the time, the traditional return to search the way began to meet the required information and access to the full range of resources and efficiency. Open relation extraction (ORE) overcomes the shortcomings of traditional information acquisition technology. Traditional information acquisition technology trained their extractors for each relationship model. There are many systems popular in English ORE, such as OLLIE, ReVerb and Exemplar. However, ORE for other languages is basically no relevant research report. The graduation design uses a system based on grammar analysis ZORE (Zh ORE) to the simplified Chinese text and semantic model of the relationship between the extraction. Zore defines the candidate relationship from the dependent tree of the automatic resolution, and then continually passes the entity's relationship and semantic pattern through a new dual-propagation algorithm.

\enkeywords{Open relation extratction, ZORE, Double propagation algorithm}
\end{enabstract}
