\begin{abstract}
在这个时代里，互联网蓬勃发展，其中的信息也随着时间日渐增多，传统的返回检索方式开始无法以高效率获取用户所需信息，并满足提供的知识资源的全面性。实体的知识关系抽取，可以从自然语言（中文文本）中抽取实体并将实体之间的关系结构化，从而提高了用户所获取信息的全面性和获取信息的效率。

信息提取（IE）系统的工作是从自然语言文本中提取语义关系，但大多数系统使用预先定义的监督学习关系例子，因此受到训练数据的限制。这种方式的信息提取必须要有精确、狭义、预先指定的要求。例如从一些会议通告里提取时间和地点。而如果在另一个领域里进行关系抽取，则需要用户对实体关系命名并手工制定新的提取规则或对新的训练集例子进行手工标注。这样的人力工作量随着目标实体关系的数量线性增加。

开放式关系抽取（Open Relation Extraction，ORE）是实体关系抽取的一种，它克服了传统信息提取（IE）的缺陷，即传统的信息获取技术需要依据每种关系模式各自训练其所属类型的提取器。

有很多系统流行于英文的 ORE，例如 OLLIE，ReVerb 和 Exemplar 等。然而，英文外的其他语言的 ORE 只有极少的相关研究的报告。本毕业设计采用基于语法分析的系统中文开放式关系抽取（ZORE，Zh ORE）系统来对简体中文文本进行关系和语义模式的抽取。ZORE 从自动解析的依存树里定义了候选的关系，然后将实体的关系和语义模式通过一种新的双重拓展算法进行处理，从而提升二者的准确性。

本文内容包括了对于所采取的实体关系抽取系统中文开放式关系抽取的介绍与其实现，以及关于中文开放式关系抽取所需组件的介绍，并根据实验对其进行评估。

\keywords{开放式关系抽取\zhspace{} 中文开放式关系抽取\zhspace{} 实体关系抽取\zhspace{} 知识库}
\end{abstract}

\begin{enabstract}
With the continuous development of the Internet, with the passage of time, more and more information, the traditional return search method began to meet the need to obtain the required information and knowledge resources needs, fully and effectively completed. The knowledge of the entity can be extracted from the natural language (Chinese text), the structure of the relationship between the entities, and improve the user's available information is comprehensive and efficient.

The information extraction (IE) system seeks to extract semantic relations text from natural language, but most systems use specific examples of supervised learning relationships, thus limiting the availability of training data. On the other hand, an open information extraction system such as TextRunner is dedicated to handling unrestricted physical relationships obtained from the Internet. Then move to another domain where the user needs to name the entity relationship and manually create the new extraction rule, or manually annotate the new training set example. The amount of artificial workload increases linearly with the number of target entities.

Open relational extraction (ORE) is an entity relationship extraction that overcomes the shortcomings of traditional information extraction (IE), the traditional information acquisition techniques for each relational model to develop their extractors. English ORE has many popular systems, such as OLLIE, ReVerb and Exemplar. However, ORE in other languages ​​is basically no relevant research report. The graduation design uses a system based on parsing. ZORE (Zh ORE) simplifies the relationship between Chinese text and semantic models. Zore defines the candidate relationship from the automatic resolution dependency tree, and then passes the entity's relationship and semantic pattern continually through the new dual-propagation algorithm.

This article introduces the introduction and implementation of the Entity Relationship Extraction System (ZORE), and introduces the components required by ZORE and applies it to the actual project.

\enkeywords{open relation extratction, ZORE, entity extraction, knowledge base}
\end{enabstract}

